---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uscore

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/probaverse/uscore/branch/main/graph/badge.svg)](https://app.codecov.io/gh/probaverse/uscore?branch=main)
<!-- badges: end -->

The goal of uscore is to calculate empirical-based scores from data. 

- `uscore()` essentially fits data so they are equally spaced between 0 and 1. 
- `nscore()` spaces data along a standard Normal distribution. 
- `rpscore()` calculates empirical return periods.

## Installation

You can install the development version of uscore like so:

``` r
remotes::install_github("probaverse/uscore")
```

## Example

Consider a numeric vector:

```{r}
library(uscore)
x <- c(0.3, 0.56, NA, 0.1, -12)
```

Uniform scores:

```{r}
uscore(x)
```

Normal scores:

```{r}
nscore(x)
```

Empirical return periods:

```{r}
rpscore(x)
```

